Alex's Notes and Text Fragments for the JSS Manuscript

### 2023-08-11 paper/article.Rmd
extend llo figure caption

```{r llo, echo=FALSE, out.width="70%", fig.cap='Birds-eye view of `"leave-location-out"` CV from package \\pkg{CAST} (method `"sptcv\\_cstf"` and column role `"space" = "SOURCEID"`).', fig.pos="ht"}
knitr::include_graphics("pdf/llo.pdf")
```

>>>>

```{r llo, echo=FALSE, out.width="70%", fig.cap='Birds-eye view of `"leave-location-out"` CV from package \\pkg{CAST} (method `"sptcv\\_cstf"` and column role `"space" = "SOURCEID"`). The readers viewpoint is located on top of the figure, looking down. The transects are individual locations being left out across multiple time steps.', fig.pos="ht"}
knitr::include_graphics("pdf/llo.pdf")
```
